Wikipedia Text Mining and Surprisal Analysis

### 2019-07-16 surprisal/wiki_surprisal.Rmd
surprisal hclust

```{r make dendrogram}
wiki <- read.csv(here("Data/wikipedia_unigrams.csv")) %>%
  select(-X) %>% 
  column_to_rownames("Language")

wiki %>% 
  dist() %>% 
  hclust() %>% 
  ggdendrogram(rotate = FALSE, size = .1) + 
  ylim(0, .10)

>>>>

```{r make dendrogram}
wiki_unigrams <- read.csv(here("Data/relative_ngrams.csv")) %>%
  filter(gram == "Unigram") %>%
  sample_n(100) %>%
  column_to_rownames("language")

wiki_unigrams %>% 
  dist() %>% 
  hclust() %>% 
  ggdendrogram(rotate = FALSE, size = .1) + 
  ylim(0, .10)
